---
title: "Map Outbreaks in Poultry and Wild Birds since early 2005"
author: "Marcel Klaassen"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: false
    code_folding: hide
    toc: false
    toc_float:
      collapsed: true
      smooth_scroll: true
editor_options: 
  chunk_output_type: inline
---

```{r initializing, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load(file="data/WOAH_PI_Rdata")
library(leaflet)
library(htmltools)
```

# Map the HPAI incidences over time

The sliders allow you to select a date ranges. You can also select a narrow range and move that range as a whole up and down the slider (e.g. using the date slider you can slide a time window so, you can look at how the HPAI epidemiology evolves across the landscape over time [i.e. a manual animation if you like]).

In the map chocolate markers are for wild birds and blue for poultry.

```{r map the outbreaks by is_wild, warning=FALSE, message=FALSE, error=FALSE, eval=TRUE}

Is <- subset(PI, select=c("Dead","Species" ,"is_wild","Date","Longitude","Latitude","sero_sub_genotype_eng"))
Is$H5 <- grepl("H5",Is$sero_sub_genotype_eng)
Is <- Is[complete.cases(Is),]
Is$markerCol <- ifelse(Is$is_wild,"chocolate","blue")
xy <- crosstalk::SharedData$new(Is)
pal <- colorFactor(
  palette = 'Paired',
  domain = Is$Order
)

#create a date slider
crosstalk::filter_slider("Outbreak Date", "Outbreak Date", xy, ~as.Date(Date), width = "90%")

#Create a checkbox filter for Order
crosstalk::filter_checkbox("wild birds", "Wild birds", xy, ~is_wild, allLevels = FALSE,inline = TRUE)

#Create a checkbox filter for H5
crosstalk::filter_checkbox("confirmed H5", "Confirmed H5", xy, ~H5, allLevels = FALSE,inline = TRUE)

leaflet::leaflet(data = xy, width = "100%") %>% addTiles %>% 
  addCircleMarkers(radius=2, color= ~markerCol, label = ~htmlEscape(paste0(Date,"-",Species))) %>% 
  addMeasure(position = "topright",primaryLengthUnit = "kilometers",primaryAreaUnit = "sqmeters",
             activeColor = "#3D535D",completedColor = "#7D4479",localization = "en")

```
